---
title: "Border Apprehension Analysis"
author: "Maria Ren, Yuehan Xiao, XuXu "
date: "2/19/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
##Summary
  Apprehension statistics record the number of foreigners who are caught while 
illegally entering the United States. These people are charged with violation of 
the Immigration and Nationality Act, and are subject to removal by the US Border Patrol.According to CNN politics, US Border Patrol reported a historic low of apprehensions under the Trump administration. 
  Our project uses the 2010 and 2017 Illegal Alien Apprehension statistical report and the Border Patrol Monthly Summary dataset to prove the decreasing number of apprehension across 9 main sectors of the US. With simple statistical tests and data analytic methods in R, our graphical analysis also shows the decreasing trend in apprehensions from 2000 to 2017. 

## Statistics Analysis 

- Comparison between 2010 and 2017 by sectors 

- Comparison between 2010 and 2017 by months

- Time Series Plot 

## Determine sectors in 2010 and 2017 with the most apprehensions 

```{r cars, echo = FALSE}
A2010<- read.csv('PB Apprehensions 2010.csv', header=TRUE, stringsAsFactors = FALSE)
A2017<- read.csv('PB Apprehensions 2017.csv', header=TRUE, stringsAsFactors = FALSE)
Monthly<- read.csv('PB monthly summaries.csv',header=TRUE, stringsAsFactors = FALSE)

```
```{r, echo= FALSE}

sector_sum_2010<-rowSums(A2010[,-1])

```
According to our calculation on 2010, Tucson is the sector with the most apprehensions, which is  212,202 apprehensions.

```{r, echo= FALSE}

max(sector_sum_2010)

```

According to our calculation on 2017, Rio Grande Valley is the sector wiht the most apprehensions, which is 137,562
```{r, echo= FALSE}
sector_sum_2017<-rowSums(A2017[,-1])
max(sector_sum_2017)
```
According to this data, we decided to do a two sample t-test between Tucson and Rio Grande Valley. 

##Two Sample T-Test For sector 
```{r, echo= FALSE}
row.names(A2010) <- A2010[,1]
A2010<-A2010[,2:13]
A2010_tucson <- as.vector(A2010[8,],mode='numeric')
row.names(A2017) <- A2017[,1]
A2017 <- A2017[,2:13]
A2017_RGV <- as.vector(A2017[6,],mode='numeric')
intake.A2010_sector <- A2010_tucson
intake.A2017_sector <- A2017_RGV
t.test(intake.A2010_sector, intake.A2017_sector)
```
Since the p-value is 0.06346 which is greater than 0.05, so we fail to reject null hypothesis. It indiates that there are no significant difference in the mean apprehensions of 2010 Tucson and 2017 Rio Grand Valley. So there is no change in the sector'smaximum. 

##Determine 3 months in 2010 with the most apprehensions 
```{r, echo=FALSE}
barplot(as.matrix(A2010), names.arg = colnames(A2010), 
        las=2,
        axisnames=TRUE,
        main="2010 Border Patrol Apprehensions by Sector",
        border="light blue",
        ylab="Apprehensions",
        xlab="Year",
        col="light blue")
```


##Determine 3 months in 2017 with the most apprehensions 
```{r, echo=FALSE}
barplot(as.matrix(A2017), names.arg = colnames(A2017), 
        las=2,
        axisnames=TRUE,
        main="2017 Border Patrol Apprehensions by Sector",
        ylab="Apprehensions",
        xlab="Year",
        border="pink",
        col="pink")

```


## Two Sample T-Test For Months
```{r, echo=FALSE}
A2010_3 <- as.vector(A2010[,6], mode='numeric' )
A2010_4 <- as.vector(A2010[,7], mode='numeric' )
A2010_5 <- as.vector(A2010[,8], mode='numeric' )
A2010_345<-as.vector(cbind(A2010_3,A2010_4,A2010_5))
A2017_10 <- as.vector(A2017[,1], mode='numeric' )
A2017_11 <- as.vector(A2017[,2], mode='numeric' )
A2017_12 <- as.vector(A2017[,3], mode='numeric' )
A2017_101112 <- as.vector(cbind(A2017_10,A2017_11,A2017_12))
intake.A2010_month <- A2010_345
intake.A2017_month <- A2017_101112
t.test(intake.A2010_month, intake.A2017_month)

```
Since the p-value is 0.2075 which is greater than 0.05, so we fail to reject null hypothesis. It indiates that there are no significant difference in the mean apprehensions of 2010 March, April and May,  and 2017 October, Novermber and December. So there is no change in the month's  maximum. 

## Time Series Plot
```{r, echo=FALSE}
row.names(Monthly) <- Monthly[,1]
Monthly<-Monthly[,2:13]
ts8 <- as.vector(t(Monthly[,-1]))
ts9 <- ts(rev(ts8), start= c(2000,1), frequency=12)
ts10 <- ts.plot(ts9, gpars=list(xlab="year", ylab="Apprehensions", lty=c(1:3)),col='purple')
#let the Monthly data turns into a matrix
ts11 <-as.matrix(Monthly)
#the function to calculate the average of each year's apprehensions
ts12 <- rev(sapply(1:18, function(i) sum(ts11[i,])/12))
namebank <- as.character(c(2000:2017))
#label the years and lines on the averaged position
text(c(2000:2017), ts12, namebank,cex=0.9)
text(c(2000:2017), ts12, labels="----", cex=0.9,pos=2, col="red" )

```
From the time series plot, we can see that the average monthly BP Apprehensions decreases across the years between 2000 and 2017.


##Citation
Kopan, Tal. “US-Mexico Border Apprehensions Hit 17-Year Lows.” CNN, Cable News Network, 9 May 2017, www.cnn.com/2017/05/09/politics/border-crossings-apprehensions-down-trump/index.html.